### 2018-08-27 analysis-note-vf/Appendix.tex
add a chapter in the appendix for the nucleon dvcs theory

>>>>

\chapter{ Angular dependence of the nucleon DVCS beam-spin asymmetry}

Note: All the formulas have been derived from A.~V.~Belitsky, D.~Mueller and 
A.~Kirchner,
  %``Theory of deeply virtual Compton scattering on the nucleon,''
Nucl.\ Phys.\ B {\bf 629}, 323 (2002).
[hep-ph/0112108].
%%CITATION = hep-ph/0112108%%

The four-fold cross section for the process $e (k) h (P_1) \to e (k^\prime) h 
(P_2) \gamma (q_2)$,

\begin{eqnarray}
\label{WQ}
\frac{d\sigma}{d\Bx dy d|\Delta^2| d\phi }
=
\frac{\alpha^3  \Bx y } {16 \, \pi^2 \,  {\cal Q}^2 \sqrt{1 + \epsilon^2}}
   \frac{ |{\cal T}_{\rm BH}|^2 + |{\cal T}_{\rm DVCS}|^2 + {\cal I} }{e^6} \, 
   .
   \eqname{eq.22\&23 in ref}
\end{eqnarray}
This cross section depends on the Bjorken variable $\Bx$, the squared
momentum transfer $\Delta^2 = (P_2 - P_1)^2$, the lepton energy fraction $y
= P_1\cdot q_1/P_1\cdot k$, with $q_1 = k - k'$, $\phi$ is the angle between 
the lepton and hadron scattering planes, and $epsilon$ is defined as
$\epsilon \equiv 2 \Bx \frac{M}{{\cal Q}}$

The BH term $|{\cal T}_{\rm BH}|^2$, squared DVCS amplitude
$|{\cal T}_{\rm DVCS}|^2$, and  interference term ${\cal I}$ read
\begin{eqnarray}
\label{Par-BH}
&&|{\cal T}_{\rm BH}|^2
= \frac{e^6}
{\Bx^2 y^2 (1 + \epsilon^2)^2 \Delta^2\, {\cal P}_1 (\phi) {\cal P}_2 (\phi)}
\left\{
c^{\rm BH}_0
+  \sum_{n = 1}^2
c^{\rm BH}_n \, \cos{(n\phi)} + s^{\rm BH}_1 \, \sin{(\phi)}
\right\} \, ,
   \eqname{eq.25 in ref}
\\
\label{AmplitudesSquared}
&& |{\cal T}_{\rm DVCS}|^2
=
\frac{e^6}{y^2 {\cal Q}^2}\left\{
c^{\rm DVCS}_0
+ \sum_{n=1}^2
\left[
c^{\rm DVCS}_n \cos (n\phi) + s^{\rm DVCS}_n \sin (n \phi)
\right]
\right\} \, ,
   \eqname{eq.26 in ref}
\\
\label{InterferenceTerm}
&&{\cal I}
= \frac{\pm e^6}{\Bx y^3 \Delta^2 {\cal P}_1 (\phi) {\cal P}_2 (\phi)}
\left\{
c_0^{\cal I}
+ \sum_{n = 1}^3
\left[
c_n^{\cal I} \cos(n \phi) +  s_n^{\cal I} \sin(n \phi)
\right]
\right\} \, ,
   \eqname{eq.27 in ref}
\end{eqnarray}
where the $+$ ($-$) sign in the interference stands for the negatively
(positively) charged lepton.

\section{Definition of some variables}

The lepton BH propagators,

\begin{eqnarray}
\label{Par-BH-Pro}
{\cal P}_1
   &=&- \frac{1}{y (1 + \epsilon^2)} \left\{ J + 2 K \cos(\phi) \right\}
\,\,
   \eqname{eq.32 in ref}
   \\
{\cal P}_2
   &=&
1 + \frac{\Delta^2}{\cQ^2} +
\frac{1}{y (1 + \epsilon^2)}\left\{J   + 2 K \cos(\phi)
\right\}
   \eqname{eq.32 in ref}
\, ,
\end{eqnarray}

where
\begin{eqnarray*}
J =
\left( 1 - y - \frac{y \epsilon^2}{2} \right)
\left( 1 + \frac{\Delta^2}{\cQ^2} \right)
-
(1 - x) (2 - y) \frac{\Delta^2}{\cQ^2} \, .
   \eqname{eq.32 in ref}
\end{eqnarray*}

\begin{equation}
K^2 = -\frac{\Delta^2}{{\cal Q}^2} (1 - \Bx)
\left( 1 - y - \frac{y^2\epsilon^2}{4} \right)
\left( 1 - \frac{\Delta^2_{\rm min}}{\Delta^2} \right)
\left\{
\sqrt{1 + \epsilon^2}
+ \frac{4\Bx (1 - \Bx) + \epsilon^2}{4(1 - \Bx)}
\frac{\Delta^2 - \Delta^2_{\rm min}}{{\cal Q}^2}
\right\} \, ,
   \eqname{eq.30 in ref}
\end{equation}

\begin{eqnarray}
\label{Def-tmin}
-\Delta_{\rm min}^2
=  {\cal Q}^2
\frac{2(1 - \Bx) \left(1 - \sqrt{1 + \epsilon^2}\right) + \epsilon^2}
{4\Bx (1 - \Bx) + \epsilon^2}
\approx \frac{M^2 \Bx^2}{1 - \Bx + \Bx M^2/{\cQ}^2}
\, ,
   \eqname{eq.31 in ref}
\end{eqnarray}

\begin{eqnarray}
y(x,\cQ^2)
=
2 \frac{\sqrt{1 + \epsilon^2} - 1}{\epsilon^2}
\approx
1 - \frac{M^2 \Bx^2}{\cQ^2} \, .
\end{eqnarray}

\section{Beam-spin asymmetry}
 At leading twist, the beam-spin asymmetry ($A_{LU}$) with two opposite 
 helicities of a  longitudinally-polarized electron beam (L) on an unpolarized 
 target (U) can be written as:

 \begin{eqnarray}
    \label{eq:coh_BSA}
    \eqname{eq.176 in ref}
A_{LU}& =& \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}\\
    \eqname{}
      & =& \frac{x_A(1+\epsilon^2)^2}{y} \, s_1^{\cal I} \sin(\phi) \, \bigg/ 
      \, \bigg[ \, \sum_{n=0}^{n=2}c_n^{BH}\cos{(n\phi)} +  \\
    & & \frac{x_A^2 t {(1+\epsilon^2)}^2}{Q^2} {\cal P}_1(\phi) {\cal 
    P}_2(\phi) \, c_0^{DVCS} + \frac{x_A (1+\epsilon^2)^2}{y} \sum_{n=0}^{n=1} 
    c_n^{\cal I} \cos{(n\phi)} \bigg].  
 \nonumber 
 \end{eqnarray}

\subsection{Rewriting $A_{LU}$ in term of $\phi$ harmonics}
$A_{LU}$ can be expressed as following

 \begin{eqnarray}
A_{LU}& =& \frac{\alpha_0 \sin(\phi)}
                {\alpha_1 +  \alpha_2 \cos(\phi) + \alpha_3 \cos(2\phi) }   
                \label{eq:coh_BSA_2}
\end{eqnarray}
with the kinematical variables $\alpha_{0,1,2,3}$ as

 \begin{eqnarray}
\alpha_{0}& =& \frac{x_A(1+\epsilon^2)^2}{y} \, {\color{blue} s_1^{\cal I}},
\nonumber\\
\alpha_{1}& =& {\color{blue} c_0^{BH}} - \frac{x_A^2 t {(1+\epsilon^2)}^2}{Q^2}  \frac{1}{y (1 + \epsilon^2)}
\left( (J+K) (1 + \frac{\Delta^2}{\cQ^2}) + \frac{J^2 + 2K^2}{y (1 + \epsilon^2)} \right) {\color{blue} c_0^{DVCS}} + \frac{x_A (1+\epsilon^2)^2}{y} {\color{blue} c_0^{\cal I}},\\
\nonumber\\
\alpha_{2}& =& {\color{blue} c_1^{BH}} + \frac{x_A (1+\epsilon^2)^2}{y} {\color{blue} c_1^{\cal I}},
\nonumber\\
\alpha_{3}& =& {\color{blue} c_2^{BH}} - \frac{x_A^2 t {(1+\epsilon^2)}^2}{Q^2}  \frac{K}{y (1 + \epsilon^2)}
\left( 1 + \frac{\Delta^2}{\cQ^2} + \frac{2K}{y (1 + \epsilon^2)} \right) {\color{blue} c_0^{DVCS} }
\nonumber\\
%\alpha_{4}& =& - \frac{x_A^2 t {(1+\epsilon^2)}^2}{Q^2}  \frac{2K}{y (1 + \epsilon^2)}
%\left( 1 + \frac{\Delta^2}{\cQ^2} + \frac{2K}{y (1 + \epsilon^2)} \right) {\color{blue} c_0^{DVCS} }.
%\nonumber\\
 \label{eq:alphas_}
\end{eqnarray}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Leading twist Fourier coefficients for unpolarized nucleon target}

\begin{itemize}
\item Bethe-Heitler coefficients
\label{BHcrosssection}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This part of the leptoproduction cross section is expressed solely in
terms of $F_1(\Delta^2)$ and $F_2(\Delta^2)$, the known Dirac and Pauli
form factors of the nucleon. For unpolarized target the Fourier
coefficients are:

\begin{eqnarray}
\label{Def-FC-BH-unp0}
    \eqname{eq.35 in ref}
c^{\rm BH}_{0,{\rm unp}}
\!\!\!&=&\!\!\!
8 K^2
\left\{
\left( 2 + 3 \epsilon^2 \right)
\frac{{\cal Q}^2}{\Delta^2}
\left( F_1^2 - \frac{\Delta^2}{4 M^2} F_2^2 \right)
+ 2 \Bx^2 \left( F_1 + F_2 \right)^2
\right\}
\\
&+&\!\!\! (2 - y)^2
\Bigg\{
\left( 2 + \epsilon^2 \right)
\Bigg[
\frac{4 \Bx^2 M^2}{\Delta^2}
\left( 1 + \frac{\Delta^2}{{\cal Q}^2} \right)^2
+ 4 (1 - \Bx)
\left( 1 + \Bx  \frac{\Delta^2}{{\cal Q}^2} \right)
\Bigg]
\left( F_1^2 - \frac{\Delta^2}{4 M^2} F_2^2 \right)
\nonumber\\
&+&\!\!\!
4 \Bx^2
\Bigg[
\Bx + \left(1 - \Bx + \frac{\epsilon^2}{2} \right)
\left(1 -  \frac{\Delta^2}{Q^2} \right)^2
- \Bx (1 - 2 \Bx) \frac{\Delta^4}{Q^4}
\Bigg]
\left( F_1 + F_2 \right)^2
\Bigg\}
\nonumber\\
&+&\!\!\! 8 \left( 1 + \epsilon^2 \right)
\left(1 - y - \frac{\epsilon^2 y^2}{4} \right)
\Bigg\{
2 \epsilon^2
\left( 1 - \frac{\Delta^2}{4 M^2} \right)
\left( F_1^2 - \frac{\Delta^2}{4 M^2} F_2^2 \right)
\nonumber\\
&&\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad
- \Bx^2
\left( 1 -  \frac{\Delta^2}{Q^2} \right)^2
\left( F_1 + F_2 \right)^2
\Bigg\} \, ,
\nonumber\\
\label{Def-FC-BH-unp1}
    \eqname{eq.36 in ref}
c^{\rm BH}_{1,{\rm unp}}
\!\!\!&=&\!\!\!
8 K (2 - y)
\Bigg\{
\left(
\frac{4\Bx^2 M^2}{\Delta^2} - 2\Bx - \epsilon^2
\right)
\left(
F_1^2 - \frac{\Delta^2}{4 M^2} F_2^2
\right)
\\
&&\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad
+ \, 2 \, \Bx^2
\left( 1 - (1 - 2\Bx) \frac{\Delta^2}{{\cal Q}^2} \right)
\left( F_1 + F_2 \right)^2
\Bigg\},
\nonumber\\
\label{Def-FC-BH-unp2}
    \eqname{eq.37 in ref}
c^{\rm BH}_{2,{\rm unp}} \!\!\!&=&\!\!\!
8 \Bx^2 K^2  \left\{ \frac{4 M^2}{\Delta^2}
\left(F_1^2 - \frac{\Delta^2}{4 M^2} F_2^2\right) + 2 \left(F_1 +
F_2\right)^2 \right\} \, .
\end{eqnarray}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item DVCS coefficients
\label{SubSec-AziAngDep-DVCS}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

$|{\cal T}_{\rm DVCS}|^2$ is bilinear in the CFFs, and its coefficients read
at leading twist and leading order for unpolarized target:

\begin{eqnarray}
\label{Def-C-DVCS-unp}
    \eqname{eq.43\&66 in ref}
c^{\rm DVCS}_{0,{\rm unp}}
\!\!\!&=&\!\!\!
   \frac{2 ( 2 - 2 y + y^2 )}{(2 - \Bx)^2}
\Bigg\{
4 (1 - \Bx)
\left(
{\cal H} {\cal H}^\ast
+
\widetilde{\cal H} \widetilde {\cal H}^\ast
\right)- \Bx^2
\bigg(
{\cal H} {\cal E}^\ast
+ {\cal E} {\cal H}^\ast
+ \widetilde{{\cal H}} \widetilde{{\cal E}}^\ast
+ \widetilde{{\cal E}} \widetilde{{\cal H}}^\ast
\bigg)
\nonumber\\
&&\qquad\qquad\;
-
\left( \Bx^2 + (2 - \Bx)^2 \frac{\Delta^2}{4M^2} \right)
{\cal E} {\cal E}^\ast
- \Bx^2 \frac{\Delta^2}{4M^2}
\widetilde{{\cal E}} \widetilde{{\cal E}}^\ast
\Bigg\},
\end{eqnarray}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\item Interference coefficients
\label{SubSec-AziAngDep-INT}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

For the phenomenology of GPDs, ${\cal I}$ is the most interesting quantity
since it is linear in CFFs. This simplifies their disentanglement from
experimental measurements. At leading twist and leading order, the Fourier 
harmonics have the following form for unpolarized target:

\begin{eqnarray}
    \eqname{eq.53 in ref}
   c^{\cal I}_{0,\rm{unp}}
   \!\!\!&=&\!\!\!
   - 8  (2 - y)
   \Re{\rm e}
   \Bigg\{
      \frac{(2 - y)^2}{1-y} K^2 {\cal C}^{\cal I}_{\rm unp} \left({\cal 
      F}\right)
      +
      \frac{\Delta^2}{{\cal Q}^2}  (1-y)(2 - \Bx)
      \left(
      {\cal C}^{\cal I}_{\rm unp} + \Delta {\cal C}^{\cal I}_{\rm unp}
      \right)
      \left( {\cal F} \right)
      \Bigg\} \, ,
    \end{eqnarray}

\begin{eqnarray}
   \label{Res-IntTer-unp_c}
    \eqname{eq.54 in ref}
   c^{\cal I}_{1, \rm unp} &\!\!\!=\!\!\!&
   -8 K (2 - 2y + y^2)~\Re{\rm e}\left\{
       {\cal C}^{\cal I}_{\rm unp}\left({\cal F} \right) \right\}
    \end{eqnarray}

\begin{eqnarray}
   \label{Res-IntTer-unp_s}
    \eqname{eq.54 in ref}
    s^{\cal I}_{1, \rm unp}
   &\!\!\!=\!\!\!&
   8 K \lambda y (2-y)~\Im{\rm m} \left\{
      {\cal C}^{\cal I}_{\rm unp}\left({\cal F} \right) \right\} \end{eqnarray}

In the lowest twist approximation, ${\cal C}^{\cal I}_{\rm unp}\left({\cal F} 
\right)$ reads

\begin{eqnarray}
   \label{Def-C-Int-unp}
    \eqname{eq.69 in ref}
   {\cal C}^{\cal I}_{\rm unp}
   \!\!\!&=&\!\!\!
   F_1 {\cal H} + \frac{\Bx}{2 - \Bx}
   (F_1 + F_2) \widetilde {\cal H}
   -
   \frac{\Delta^2}{4M^2} F_2 {\cal E} \, ,
\end{eqnarray}

The addenda arising in power-suppressed contribution is defined as

\begin{eqnarray}
   \label{Def-C-IntAdd-unp}
    \eqname{eq.72 in ref}
   \Delta {\cal C}^{\cal I}_{{\rm unp}}
   \!\!\!&=&\!\!\!
   - \frac{\Bx}{2-\Bx}  (F_1 + F_2)
   \left\{
      \frac{\Bx}{2 - \Bx} ({\cal H} + {\cal E})
      + \widetilde {\cal H}
      \right\} \, ,
\end{eqnarray}

\subsection{Definition of the CFFs}
The Compton form factors (CFFs), $\mathcal{F = \{ H, E, \widetilde{H}, 
\widetilde{E}}\}$, are defined in terms of the GPDs, $F = \{H, E, 
\widetilde{H}, \widetilde{E}\}$ ,as:

\begin{align}
\begin{split}
    \eqname{}
\Re(&\mathcal{F}) = \mathcal{P} \int_{0}^{1}dx[F(x,\xi,t)-F(-x,\xi,t)] \, 
C^{\pm}(x,\xi), \end{split} \\
\Im(&\mathcal{F}) = - \pi [F(\xi,\xi,t)-F(-\xi,\xi,t)],
\end{align}

\subsection{Definition of $\phi$}
The angle between the leptonic and the hadronic planes, $\phi$, is defined as:

\begin{equation}
  \cos(\phi) = \frac{\vec{k} \times \vec{k'}}{| \vec{k} \times \vec{k'} |} 
   \cdot \frac{\vec{q} \times \vec{p'}}{| \vec{q} \times \vec{p'} |}
\end{equation}
and $\phi \in [0,\phi] iff (\vec{k} \times \vec{k'}).\vec{q'} \geq 0$.

Where $\vec{k}/\vec{k'}$, $\vec{q}/\vec{q'}$, $\vec{p}/\vec{p'}$ are the 
four-vectors of the incident/scatter electrons, virtual/real photons, 
initial/final protons.
